14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-07-03 rules/rules19.tex
Clarified the unsat-core track scoring
Add single query results.

  \item {\bf Competition-Wide Recognitions.}
    This year, we will replace the previous notion of competi\-tion-wide scoring
    as introduced for the Main Track in 2014 (and improved over the years)
    with recognitions for all tracks that do not directly compare divisions.
    \rationale{Competition-wide scoring was introduced as a metric to
    compare solver performance across all divisions. By definition, this metric
    is biased towards solvers that enter a large number of divisions.}

>>>>

  \item {\bf Competition-Wide Recognitions.}
    This year, we will replace the previous notion of competi\-tion-wide scoring
    as introduced for the Main Track in 2014 (and improved over the years)
    with recognitions for all tracks that do not directly compare divisions.
    \rationale{Competi\-tion-wide scoring was introduced as a metric to
    compare solver performance across all divisions. It is, by definition,
    biased towards solvers that enter a large number of divisions.}
